A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-01-29 archive/v3/docs_v3/introduction_v3.02.tex
Cleaned up (files are moved to archive now)

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in F450W}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in F814W}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{The lensing images}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar Kinematics by \citet{SWELLSV}}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The black solid line in panel (b) shows the orientation of the major-axis. Its length is $10''$ and it indicates approximately where we carry out the dynamical modelling. \emph{Panel (c):} Lensing images in the central region of J1331.  An IRAF \emph{ellipse} fit to the F450W surface brightness in panel (a) was subtracted from the image. The (smoothed) residuals within the white square in panel (a) are shown in panel (c). (The four bright blobs (A,B,C and D), that become visible, are arranged in a typical strong lensing configuration around the center of the galaxy (G). The configuration of the two additional blobs, that lie approximately on a line with A, B and G, does not suggest that they form a lensing doublet. They might be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$. The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2~\text{kpc}$. The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
\label{fig:specialJ1331}
\end{figure*}

>>>>

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in the F450W filter.}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in the F814W filter.}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{Lensing images around the galaxy center.}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar kinematics by \citet{SWELLSV}.}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3628 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The black solid line in panel (b) shows the orientation of the major-axis. Its length is $10''$ and it marks approximately the region within which we carry out the dynamical modelling. \emph{Panel (c):} Lensing images in the central region of J1331.  An IRAF \emph{ellipse} model was fitted to and then subtracted from the galaxy's F450W surface brightness in panel (a). The (smoothed) residuals within the white square in panel (a) are shown in panel (c). The four bright blobs (A, B, C and D) which are visible in the residuals are arranged in a typical strong lensing configuration around the center of the galaxy (G). (The configuration of the two additional blobs which lie approximately on a line with A, B and G does not suggest that these blobs are a lensing doublet. They might rather be star forming regions of a background galaxy.) \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}. Shown are line-of-sight rotation velocity $v_\text{rot}$ (top), line-of-sight velocity dispersion $\sigma$ (middle) and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$ (bottom). The dashed line indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6'' = 5.2~\text{kpc}$. The $v_\text{rot}$ curve reveals that J1331 has a counter-rotating core within $R_\text{eff}$.}
\label{fig:specialJ1331}
\end{figure*}

### 2016-01-29 archive/v3/docs_v3/model_MGE_v3.02.tex
Cleaned up (files are moved to archive now)

\paragraph{Multi-Gaussian Expansion (MGE).} MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ two-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}. This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap02}. We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured counter-clockwise from the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$. Then the surface brightness can be written as
\begin{eqnarray}
I(R',\theta') &=& \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
\text{and } x'_i &=& R' \cos(\theta' - \phi)\nonumber\\
y'_i &=& R' \sin(\theta' - \phi),\nonumber
\end{eqnarray}
where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussians major and minor axis.

We can also expand the telescopes point-spread function (PSF) as a sum of circular Gaussians,
\begin{equation}
\text{PSF}(x',y') = \sum_j \frac{G_j}{2 \pi \delta_j^2} \exp\left[- \frac{1}{2 \delta_j^2} \left({x'}^2 + {y'}^2 \right)\right], \label{eq:PSFgeneral}
\end{equation}
where $\sum_j G_j = 1$ and $\delta_j$ are in this case the dispersions of the circular PSF Gaussians. In this case the observed surface brightness distribution is a convolution of the intrinsic surface brightness in Equation \ref{eq:MGEgeneral} with the PSF in Equation \ref{eq:PSFgeneral}: $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.

>>>>

\paragraph{Multi-Gaussian Expansion (MGE).} MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ 2-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}. This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap02}. We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured counter-clockwise from the $y'$-axis of the coordinate system with polar coordinates $(R',\theta')$. Then the surface brightness can be written as
\begin{eqnarray}
I(R',\theta') &=& \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
\text{and } x'_i &=& R' \cos(\theta' - \phi)\nonumber\\
y'_i &=& R' \sin(\theta' - \phi),\nonumber
\end{eqnarray}
where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussian's major and minor axis.

We can also expand the telescope's point-spread function (PSF) as a sum of circular Gaussians,
\begin{equation}
\text{PSF}(x',y') = \sum_j \frac{G_j}{2 \pi \delta_j^2} \exp\left[- \frac{1}{2 \delta_j^2} \left({x'}^2 + {y'}^2 \right)\right], \label{eq:PSFgeneral}
\end{equation}
where $\sum_j G_j = 1$ and $\delta_j$ are in this case the dispersions of the circular PSF Gaussians.

The observed surface brightness distribution is a convolution of the intrinsic surface brightness in Equation \eqref{eq:MGEgeneral} with the PSF in Equation \eqref{eq:PSFgeneral}: $(I \ast \text{PSF}) (x',y')$ is then again a sum of Gaussians and can be directly fitted to an image of the galaxy in question.

### 2016-01-29 archive/v3/docs_v3/model_lensing_v3.01.tex
Cleaned up (files are moved to archive now)

\paragraph{Model fitting.} The free parameters of the lens model are: the source position $(\xi,\eta)$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel} and \eqref{eq:Fourieransatz}. We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$. To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $. The best fit lens model is then the one that minimizes
\begin{eqnarray*}
\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\\
&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,
\end{eqnarray*}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation*}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} 
\end{equation*}
which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation*}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape}
\end{equation*}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.

>>>>

\paragraph{Model fitting.} The free parameters of the lens model are: the source position $(\xi,\eta)$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel} and \eqref{eq:Fourieransatz}. We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$. To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $. The best fit lens model is then the one that minimizes
\begin{eqnarray}
\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\nonumber\\
&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} \xi - \tilde{\xi}_i \\ \eta - \tilde{\eta}_i \end{matrix} \right) \right|^2,\label{eq:chi2lens}
\end{eqnarray}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{\xi}_i,\tilde{\eta}_i)$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} \label{eq:chi2shape}
\end{equation}
which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape} \label{eq:chi2total}
\end{equation}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.

### 2016-01-29 archive/v3/docs_v3/results_JAMwithNFW_v3.02.tex
Cleaned up (files are moved to archive now)

%=======================
\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue). The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse). The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}. \Wilma{[TO DO: Maybe mention also: There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior. ]}}
\label{fig:modelB4_triangle}
\end{figure*}
%=======================

@@

%==============
\begin{figure*}
\centering
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{\Wilma{[TO DO: Rewrite caption]} Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey). \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
\label{fig:modelB4_models}
\end{figure*}
%==============

@@

\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first error is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation*}
p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
\end{equation*}

We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
\begin{equation*}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
\end{equation*}

For the velocity anisotropy parameter $\beta_z$ we will again employ a uniform prior 
\begin{equation*}
p(\beta) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.

>>>>

%=======================
\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with an MCMC (red dots and histograms) for a JAM model fitted to the stellar $v_\text{rms}$ data, with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green, see Equation \eqref{eq:prior_v200}) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue, see Equation \eqref{eq:prior_c200}). We find slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$) and the more velocity anisotropy is needed to reproduce the central $v_\text{rms}$ dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior.\\The MCMC samples are colour coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance matrix of the MCMC samples and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse) confidence. The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
\label{fig:modelB4_triangle}
\end{figure*}
%=======================

@@

%==============
\begin{figure*}
\centering
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit} found as best fit to the stellar $v_\text{rms}$ data (blue dots) within $\sim3.5''$. \Wilma{[TO DO: Rewrite caption]}  The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey). \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
\label{fig:modelB4_models}
\end{figure*}
%==============

@@

\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. Using the stellar mass estimate for J1331 from \citet{SWELLSI}, $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first error is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation}
p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}). \label{eq:prior_v200}
\end{equation}

We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
\begin{equation}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right). \label{eq:prior_c200}
\end{equation}

For the velocity anisotropy parameter $\beta_z$ we will again employ a uniform prior 
\begin{equation*}
p(\beta_z) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
